Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-04 doc/LinksToDAG.tex
merged the table. for now.
clarification in last paragraph before conclusions

The main vexation is the handling of subject-verb links.  Under the English link grammar, the verb (or 0) that governs a clause will link to both the clause's subject and its last (main) verb.  This ought to give us the desired treatment of {\em ``Jill persuaded him to skip''}, in which {\em ``him''} has two parents.  Unfortunately, we get {\em him} $\rightarrow$ {\em to}, because of inconsistencies in the link grammar itself.\footnote{When the subject is missing ({\em ``Jill wanted to skip''}), the governing verb now links instead to the clause's first (tensed) verb but {\em no longer} to the last as well.  That favors a consistent solution where each auxiliary verb is a parent of the verb to its right ({\em to} $\rightarrow$ {\em skip}).  As a result, when the subject is present, it must be the {\em parent} of the first verb, which otherwise would not have a parent ({\em him} $\rightarrow$ {\em to} $\rightarrow$ {\em skip}).  (Yet subjects are not {\em always} parents.  The occasional construction {\em ``It was impossible, they said''} is handled inconsistently by the link grammar:
the subject ({\em ``they''}) links only to the verb ({\em ``said''}) and so must be its child, no other parent being available.)}

@@

% Uncomment this to add in all of the parses. Warning: compilation will take a long time.
\input{figure/parses.tikz}

>>>>

The main vexation is the handling of subject-verb links.  Under the English link grammar, the verb (or 0) that governs a clause will link to both the clause's subject and its last (main) verb.  This would permit our desired treatment of {\em ``Jill persuaded him to skip''}, in which {\em ``him''} has two parents.  But the ILP solution generally treats subjects as {\em parents} of verbs (thus we get {\em him} $\rightarrow$ {\em to}), owing to inconsistencies in the link grammar itself.\footnote{Why?  When the subject is missing ({\em ``Jill wanted to skip''}), the governing verb now links instead to the clause's first (tensed) verb but {\em no longer} to the last as well.  That means that a VP must be headed by its first verb ({\em to} $\rightarrow$ {\em skip}).  As a result, when the subject is present, it must be the {\em parent} of the first verb ({\em him} $\rightarrow$ {\em to} $\rightarrow$ {\em skip}), since no other parent is available.  ({\em Note:} Subjects are not {\em always} parents.  The construction {\em ``It was impossible, they said''} is handled inconsistently by the link grammar:
the subject ({\em ``they''}) links only to the verb ({\em ``said''}) and so must be its child, no other parent being available.)}

@@

% Uncomment this to add in all of the parses. Warning: compilation will take a long time.
%\input{figure/parses.tikz}
